Exploring Local Explanations of Nonlinear Models Using Animated Linear Projections

### 2022-02-06 _paper.rmd
installation

The package can be installed from GitHub using the following __R__ code:

```{r eval=FALSE, echo=TRUE}
# install.packages("remotes") # if you don't have it
remotes::install.packages("cheem", dependencies = TRUE)
library("cheem")
run_app()
```

@@

```{r eval=FALSE, echo=TRUE}
remotes::install_github('ModelOriented/treeshap')
```

>>>>

Version 0.2.0 of the package can be installed from CRAN using the following __R__ code:

```{r eval=FALSE, echo=TRUE}
install.packages("cheem", dependencies = TRUE)
library("cheem")
run_app()
```

@@

```{r eval=FALSE, echo=TRUE}
# install.packages("remotes") # if you don't have it
remotes::install_github('ModelOriented/treeshap')
```

### 2022-02-06 _paper.tex
installation

The package can be installed from GitHub using the following \textbf{R} code:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# install.packages("remotes") \# if you don\textquotesingle{}t have it}
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install.packages}\NormalTok{(}\StringTok{"cheem"}\NormalTok{, }\AttributeTok{dependencies =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{library}\NormalTok{(}\StringTok{"cheem"}\NormalTok{)}
\FunctionTok{run\_app}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install\_github}\NormalTok{(}\StringTok{\textquotesingle{}ModelOriented/treeshap\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

>>>>

Version 0.2.0 of the package can be installed from CRAN using the following \textbf{R} code:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{install.packages}\NormalTok{(}\StringTok{"cheem"}\NormalTok{, }\AttributeTok{dependencies =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{library}\NormalTok{(}\StringTok{"cheem"}\NormalTok{)}
\FunctionTok{run\_app}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# install.packages("remotes") \# if you don\textquotesingle{}t have it}
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install\_github}\NormalTok{(}\StringTok{\textquotesingle{}ModelOriented/treeshap\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
